Extended Data

### 2021-11-16 doc/manuscript/Dow_Extended_Data.Rmd
fix up extended data table 2
#90

## table captions
species_table_caption <-"Extended Data Table 1 | Dominant ring- and diffuse-porous species at the Smithsonian Conservation Biology Institute (SCBI) and Harvard Forest, along with sample sizes included in this analysis."
mean_growth_parameters_caption = "Extended Data Table 2 | Summary of parameters describing the phenology and rate of growth for ring- and diffuse- porous species at SCBI and Harvard Forest."
tree_ring_summary_caption =  "Extended Data Table 3 | Summary of tree-ring chronologies analyzed and number of significant (at p=0.05) positive or negative correlations to monthly $T_{max}$ in univariate and multivariate analyses."

@@

```{r mean_growth_parameters_table,  eval=TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
mean_growth_parameters <- read.csv("tables_figures/phenology_parameters.csv",  col.names = c("", "ring","diffuse","ring", "diffuse"), stringsAsFactors = FALSE, check.names = FALSE)
kable(mean_growth_parameters, caption = mean_growth_parameters_caption ,  format = "latex", booktabs = TRUE,  escape = F) %>%
add_header_above(c(" ",  "SCBI" = 2, "Harvard Forest"=2 )) %>%
    column_spec(1, width = "4cm") %>%
    pack_rows("Stem Growth", 1, 8, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
    pack_rows("Canopy Foliage (ecosystem level)", 9, 12, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
    pack_rows("Phenological sensitivity to mean max. T in critical T window (days/°C)", 13, 22, latex_gap_space = "1em", colnum = 5, hline_before = FALSE) %>%
    add_indent(14:17)%>%
    add_indent(19:22)%>%
kable_styling(latex_options = c("scale_down", "hold_position"), protect_latex = T) 
```

>>>>

## table captions
species_table_caption <-"Extended Data Table 1 | Dominant ring- and diffuse-porous species at the Smithsonian Conservation Biology Institute (SCBI) and Harvard Forest, along with sample sizes included in this analysis."
mean_growth_parameters_caption = "Extended Data Table 2 | Summary of parameters describing the phenology and temperature senisitivity of ring- and diffuse- porous species groups at the Smithsonian Conservation Biology Institute (SCBI) and Harvard Forest."
tree_ring_summary_caption =  "Extended Data Table 3 | Summary of tree-ring chronologies analyzed and number of significant (at p=0.05) positive or negative correlations to monthly $T_{max}$ in univariate and multivariate analyses."

@@

```{r mean_growth_parameters_table,  eval=TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
mean_growth_parameters <- read.csv("tables_figures/phenology_parameters.csv",  col.names = c("", "ring-porous","diffuse-porous","ring-porous", "diffuse-porous"), stringsAsFactors = FALSE, check.names = FALSE)
kable(mean_growth_parameters, caption = mean_growth_parameters_caption ,  format = "latex", booktabs = TRUE,  escape = F) %>%
add_header_above(c(" ",  "SCBI" = 2, "Harvard Forest"=2 )) %>%
    column_spec(1, width = "4cm") %>%
    pack_rows("Stem Growth", 2, 8, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
    pack_rows("Canopy Foliage (ecosystem level)", 9, 12, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
    pack_rows("Phenological temperature sensitivity* (days/°C)", 13, 22, latex_gap_space = "1em", colnum = 5, hline_before = FALSE) %>%
    add_indent(14:17)%>%
    add_indent(19:22)%>%
kable_styling(latex_options = c("scale_down", "hold_position"), protect_latex = T) 
```
*Phenological temperature sensitivity refers to the sensitivity of a parameter to the mean maximum temperature ($T_{max}$) during the critical temperature window (Fig. 1).
